Chemistry of the Orphan Stream I: Identifying Stream Members \\ from Low-Resolution Spectroscopy

### 2012-09-16 2012-oss-mrs/draft-oss-mrs.tex
Fixed ???? resolution to {1}-resolution

\begin{abstract}
We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Anglo-Astronomical Telescope. With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members. Our data indicates an overall stream metallicity of [Fe/H] $= -1.71$ with an intrinsic dispersion of $\sigma = 0.56$\,dex which is more metal-rich than previously found and unbiased by spectral type. The metallicity dispersion in our stream sample suggests that the unidentified Orphan Stream parent is a dSph satellite. We find a revised stream distance of $23.5 \pm 1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 00.0$\,km s$^{-1}$. The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that at least along the line-of-sight, the Orphan Stream is kinematically quite cold. We highlight likely members for high resolution spectroscopic follow-up.
\end{abstract}

>>>>

\begin{abstract}
We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low-resolution spectroscopic data taken with AAOmega on the Anglo-Astronomical Telescope. With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members. Our data indicates an overall stream metallicity of [Fe/H] $= -1.71$ with an intrinsic dispersion of $\sigma = 0.56$\,dex which is more metal-rich than previously found and unbiased by spectral type. The metallicity dispersion in our stream sample suggests that the unidentified Orphan Stream parent is a dSph satellite. We find a revised stream distance of $23.5 \pm 1.0$\,kpc near the celestial equator, and our kinematic signature peaks at $V_{GSR} = 00.0$\,km s$^{-1}$. The observed velocity dispersion of our highest probability members is consistent with arising from the velocity uncertainties alone, indicating that at least along the line-of-sight, the Orphan Stream is kinematically quite cold. We highlight likely members for high-resolution spectroscopic follow-up.
\end{abstract}
